Brief notes on erosion

### 2022-10-13 docs/proposals/NSF/budgets/budgetJust_Colgate.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of 
co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. 
Co-PI Moore's salary will in years 1,2,3 will be USNA Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    co-PI Moore & $\$9,585$ & $\$9,762$ & $\$9,977$  & $\$29,324$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,259$ & $\$3,319$ & $\$3,392$ & $\$9,970$ \\
    \hline
    co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
    \hline
    Total & $\$3,547$ & $\$3,612$ & $\$3,691$ & $\$10,850$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to partially fund a domestic trip
for co-PI Moore in years 2 and 3.  The expected costs per
conference participant is $\$1,000$ with a breakdown of $\$300$ for
airfare, $\$300$ for lodging, $\$56$ for local transportation, $\$144$
for meals (four days at $\$36$ per day), and $\$200$ for conference
registration.  Potential meeting venues include several SIAM Meetings
(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
appropriately themed workshops.  Alternatively, co-PI Moore may use
these travel funds to visit PI Quaife and the funded graduate student at
FSU in order to collaborate on the project.  Travel funds for the first
year are removed due to the COVID crisis.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Travel &  & $\$1,000$ & $\$1,000$ & $\$2,000$ \\
    \hline
  \end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$13,132$ & $\$14,374$ & $\$14,668$ & $\$42,174$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
The US Naval Academy's indirect cost rate is 10\% for research on
modified total direct costs (MTDC).  The base for overhead is
$\$13,132$ in year 1, $\$14,374$ in year 2, and $\$14,668$ in
year 3.  The US Naval Academy defines a fiscal year to be October 1-September
30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$1,313$ & $\$1,437$ & $\$1,467$ & $\$4,217$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$14,445$ & $\$15,811$ & $\$16,135$ & $\$46,391$ \\
    \hline
  \end{tabular}
\end{center}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of 
co-PI Moore's summer salary in year 3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. 
Co-PI Moore's summer salary will in year 3 will be \$93,788.
with the monthly salary listed in the table:
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|}
    \hline
    & Year 3  & Total \\
    \hline
    co-PI Moore & $\$10,421$  & $\$10,421$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at Colgate University are 32\%.  \\
%In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|}
    \hline
    & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,335$ & $\$3,335$ \\
    \hline
    %co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
    \hline
    Total & $\$3,335$ & $\$3,335$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to partially fund a domestic trip
for co-PI Moore in year 3.  The expected costs per
conference participant is $\$1,000$ with a breakdown of $\$300$ for
airfare, $\$300$ for lodging, $\$56$ for local transportation, $\$144$
for meals (four days at $\$36$ per day), and $\$200$ for conference
registration.  Potential meeting venues include several SIAM Meetings
(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
appropriately themed workshops.  Alternatively, co-PI Moore may use
these travel funds to visit PI Quaife and the funded graduate student at
FSU in order to collaborate on the project.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 3 & Total \\
    \hline
    Domestic Travel & $\$1,000$ & $\$1,000$ \\
    \hline
  \end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 3 & Total \\
    \hline
    $\$14,756$ & $\$14,756$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
Colgate University's indirect cost rate is 35\% for research on
modified total direct costs (MTDC).  The base for overhead is $\$14,756$ in
year 3.  
%The US Naval Academy defines a fiscal year to be October 1-September 30.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 3 & Total \\
    \hline
    $\$5,165$ & $\$5,165$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 3 & Total \\
    \hline
    $\$19,921$ & $\$19,921$ \\
    \hline
  \end{tabular}
\end{center}
